---
title: "proj10iguess"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(signal)
library(ggplot2)
library(R.matlab)
library(randomForest)
library(fastICA)
library(coroICA)
library(plyr)
knitr::opts_chunk$set(echo = TRUE)
```

## Loading the data

Has been preprocessed : filtered for each subject. Car'd.

```{r}
load('TMs.Rdata')
load('TYs.Rdata')
```

## Sets, scaling+centering

Train/testsets. Change this one as we please:

```{r}
Xtrains=rbind(M1,M2,M3,M4,M5,M6,M7,M8)
Xtests=M9
Ytrains=rbind(T1Ys,T2Ys,T3Ys,T4Ys,T5Ys,T6Ys,T7Ys,T8Ys)
Ytests=T9Ys

Xtrains=rbind(M1,M2,M3,M4,M5,M6,M7,M9)
Xtests=M8
Ytrains=rbind(T1Ys,T2Ys,T3Ys,T4Ys,T5Ys,T6Ys,T7Ys,T9Ys)
Ytests=T8Ys
```

Center+scale:
```{r}
for (i in 1:dim(M1)[2]){ #i in 1:22. Center and scale all features.
  Xtrains[,i]=(Xtrains[,i]-mean(Xtrains[,i]))/sd(Xtrains[,i])  
  Xtests[,i]=(Xtests[,i]-mean(Xtests[,i]))/sd(Xtests[,i])  
}

```


## PCA.

Note that fastICA already does PCA so we mostly do this for coroICA (and for dimension).

```{r}
colnames(Xtrains)=1:22
colnames(Xtests)=1:22
MP=preProcess(Xtrains,method='pca',thresh=0.95)
MPa=predict(MP,Xtrains) #PCAcomp for training set
Ndims=dim(MPa)[2]
MP2=preProcess(Xtests,method='pca',pcaComp=Ndims)
MP2a=predict(MP2,Xtests) #PCAcomp for test set
```

## fastICA


```{r}
Str=fastICA(Xtrains,n.comp=Ndims) #train
StrS=Str$S #S_train signals
SteS=MP2a%*%Str$W #S_test from W_train
SteS2=t(Str$W%*%t(MP2a))
```
alternatively try #SteS=t(Str$W%*%t(Mpa2))
$$
SteS=P_{CA}\times W\\
SteS_2=(W\times P_{CA}^T)^T=P_{CA}\times W^T
$$
Hence these are infact not the same! $$W\neq W^T$$



Taking the bandpower:
```{r}
Mtrains=matrix(NA,nrow=dim(Ytrains)[1],ncol=Ndims)
Mtests=matrix(NA,nrow=dim(Ytests)[1],ncol=Ndims)
Mtests2=matrix(NA,nrow=dim(Ytests)[1],ncol=Ndims)
for(i in 1:dim(Ytrains)[1]){
  Mtrains[i,]=log(diag(var(StrS[1:750+(i-1)*750,]))) #band power
}
for(i in 1:dim(Ytests)[1]){
  Mtests[i,]=log(diag(var(SteS[1:750+(i-1)*750,]))) #band power
}
for(i in 1:dim(Ytests)[1]){
  Mtests2[i,]=log(diag(var(SteS2[1:750+(i-1)*750,]))) #band power
}

```

Instead of diag(var) we may compute just the variance i guess? Should be slightly faster

```{r}
Trainset=cbind(Ytrains[,2],Mtrains)
Testset=cbind(Ytests[,2],Mtests)
Testset2=cbind(Ytests[,2],Mtests2)
rf1=randomForest(y=as.factor(Trainset[,1]),x=Trainset[,-1])
print(rf1)

ficate1=mean(predict(rf1,newdata=Testset[,-1])==Testset[,1]) #26 big meh
ficate2=mean(predict(rf1,newdata=Testset2[,-1])==Testset2[,1]) #26 big meh
c(ficate1,ficate2)
```

both do decent i suppose. 32,36

Should only really be doing one though (the correct one)..


## coroICA

Using the PCA from before

dim(MPa)

```{r}
Ctr=coroICA(MPa,partitionsize=48*750,groupsize=750*48*6,n_components=Ndims,max_iter = 10000,pairing = 'neighbouring') 
#train #compiles forever. does compile eventually. 
#Cte=coroICA(pcaTestscomp,partitionsize=48*750,groupsize=48*6*750,n_components=Ndim,max_iter=10000,pairing='neighbouring') #test
cat('converged=',Ctr$converged)
```
So Ctr is our coroICA item.  (should have converged) (did not converge now...) (previously converged after 6k).


Perhabs does not converge everytime. Maybe what they (in python?) keep track of with failedICA

View(Ctr)

```{r}
CtrS=Ctr$Shat
MStrains=matrix(NA,nrow=dim(Ytrains)[1],ncol=Ndims)
MStests=matrix(NA,nrow=dim(Ytests)[1],ncol=Ndims)
MStests2=matrix(NA,nrow=dim(Ytests)[1],ncol=Ndims)

for(i in 1:dim(Ytrains)[1]){
  MStrains[i,]=log(diag(var(CtrS[1:750+(i-1)*750,]))) #band power
}

test2=t(Ctr$V%*%t(MP2a))  #looks silly! but works. should be doing this i imagine!!
#or.. MP2A%*%V? as below
test3=MP2a%*%Ctr$V 

for(i in 1:dim(Ytests)[1]){
  MStests[i,]=log(diag(var(test2[1:750+(i-1)*750,]))) #band power
}

for(i in 1:dim(Ytests)[1]){
  MStests2[i,]=log(diag(var(test3[1:750+(i-1)*750,]))) #band power
}

temp1=cbind(Ytrains[,2],MStrains)
temp2=cbind(Ytests[,2],MStests)
temp3=cbind(Ytests[,2],MStests2)

rfc1=randomForest(y=as.factor(temp1[,1]),x=temp1[,-1]) #OOB error rate 62%
print(rfc1) 

cicate=mean(predict(rfc1,newdata=temp2[,-1])==temp2[,1]) #test accuracy 32. despite non-convergence. issa okay?
cicate2=mean(predict(rfc1,newdata=temp3[,-1])==temp3[,1]) #test accuracy 32. despite non-convergence. issa 
```



```{r}
cat('fastICA test accuracy=',ficate1, 'or',ficate2)
cat('coroICA test accuracy=',cicate,'or',cicate2) #prolly first..
cat('converged',Ctr$converged)
```

