---
title: "save/load data"
output: html_document
---

rm()

```{r setup, include=FALSE}
library(caret)
library(signal)
library(ggplot2)
library(R.matlab)
library(randomForest)
library(fastICA)
library(coroICA)
library(plyr)
knitr::opts_chunk$set(echo = TRUE)
```

## preproc
Here is how we load/save the data:
Loading the data: Only looking at T-files for now (excluding E-files)
Only need first 22 channels and last 6 runs

```{r}
T1 <- readMat('data/A01T.mat')
T1=(unlist(T1,recursive="F"))
T2 <- readMat('data/A02T.mat')
T2=(unlist(T2,recursive="F"))
T3 <- readMat('data/A03T.mat')
T3=(unlist(T3,recursive="F"))
T4 <- readMat('data/A04T.mat')
T4=(unlist(T4,recursive="F"))
T5 <- readMat('data/A05T.mat')
T5=(unlist(T5,recursive="F"))
T6 <- readMat('data/A06T.mat')
T6=(unlist(T6,recursive="F"))
T7 <- readMat('data/A07T.mat')
T7=(unlist(T7,recursive="F"))
T8 <- readMat('data/A08T.mat')
T8=(unlist(T8,recursive="F"))
T9 <- readMat('data/A09T.mat')
T9=(unlist(T9,recursive="F"))
```
or alternative 
save(T1,T2,T3,T4,T5,T6,T7,T8,T9,file='Tfiles.Rdata')
load('Tfiles.Rdata')


we define 
xTiRj to be the i'th person with run 'j
likeiwse 
xTiRjY to be the i'th person with run 'j - starting times,labels and "artifacting"

Will want to apply method b) here and use coroICA probably!

```{r,echo=T,include=T}
for (j in 4:9){
  assign(paste0("xT1R", j-3),(unlist(T1[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT2R", j-3),(unlist(T2[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT3R", j-3),(unlist(T3[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT5R", j-3),(unlist(T5[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT6R", j-3),(unlist(T6[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT7R", j-3),(unlist(T7[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT8R", j-3),(unlist(T8[[j]],recursive = F)[[1]][,1:22]))
  assign(paste0("xT9R", j-3),(unlist(T9[[j]],recursive = F)[[1]][,1:22]))
}
for (j in 2:7){
  assign(paste0("xT4R", j-1),(unlist(T4[[j]],recursive = F)[[1]][,1:22]))
}

##########

#View(T1[[4]]) #DATA4 #so we can get $data4 with [[4]]
for (j in 4:9){
  assign(paste0("xT1RY", j-3),(cbind(T1[[j]][[1]][[2]],T1[[j]][[1]][[3]],T1[[j]][[1]][[6]])))
  assign(paste0("xT2RY", j-3),(cbind(T2[[j]][[1]][[2]],T2[[j]][[1]][[3]],T2[[j]][[1]][[6]])))
  assign(paste0("xT3RY", j-3),(cbind(T3[[j]][[1]][[2]],T3[[j]][[1]][[3]],T3[[j]][[1]][[6]])))
  assign(paste0("xT5RY", j-3),(cbind(T5[[j]][[1]][[2]],T5[[j]][[1]][[3]],T5[[j]][[1]][[6]])))
  assign(paste0("xT6RY", j-3),(cbind(T6[[j]][[1]][[2]],T6[[j]][[1]][[3]],T6[[j]][[1]][[6]])))
  assign(paste0("xT7RY", j-3),(cbind(T7[[j]][[1]][[2]],T7[[j]][[1]][[3]],T7[[j]][[1]][[6]])))
  assign(paste0("xT8RY", j-3),(cbind(T8[[j]][[1]][[2]],T8[[j]][[1]][[3]],T8[[j]][[1]][[6]])))
  assign(paste0("xT9RY", j-3),(cbind(T9[[j]][[1]][[2]],T9[[j]][[1]][[3]],T9[[j]][[1]][[6]])))
}
for (j in 2:7){
  assign(paste0("xT4RY", j-1),(cbind(T4[[j]][[1]][[2]],T4[[j]][[1]][[3]],T4[[j]][[1]][[6]])))
}

```

# Filtering
5 seconds of a 25 Hz signal with slow drift, sampling frequency 250 Hz


```{r}
coefs <- butter(3, c(8 / (.5 * 250), 30 / (.5 * 250)), "pass")

```

Now each L_i is a list for a subject (i=1..9). Containing all 6 runs - each as a matrix


<!-- for (i in 1:2){ -->
<!--   print(dim(eval(as.name(paste0('xT1R',i))))) -->
<!-- } 
THIS also works
-->
750*48 rows instead



```{r}
#could do 6x9 here - so that for each subject. ..
for(i in 1:9){
#    assign(paste0("L", i),list(NA,NA,NA,NA,NA,NA))
    assign(paste0("M", i),matrix(NA,nrow=48*750*6,ncol=22))
}

for(l in 1:9){  
    tmp1=matrix(NA,nrow=750*48,ncol=22)
    tmp2=matrix(NA,nrow=750*48,ncol=22)
    tmp3=matrix(NA,nrow=750*48,ncol=22)
    tmp4=matrix(NA,nrow=750*48,ncol=22)
    tmp5=matrix(NA,nrow=750*48,ncol=22)
    tmp6=matrix(NA,nrow=750*48,ncol=22)
    for (i in 1:48){
      for (j in 1:22){
         tmp1[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R1')))[(eval(as.name(paste0('xT',l,'RY1')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY1')))[i,1]+1500),j]
         tmp2[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R2')))[(eval(as.name(paste0('xT',l,'RY2')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY2')))[i,1]+1500),j]
         tmp3[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R3')))[(eval(as.name(paste0('xT',l,'RY3')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY3')))[i,1]+1500),j]
         tmp4[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R4')))[(eval(as.name(paste0('xT',l,'RY4')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY4')))[i,1]+1500),j]
         tmp5[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R5')))[(eval(as.name(paste0('xT',l,'RY5')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY5')))[i,1]+1500),j]
         tmp6[((1:750)+750*(i-1)),j]=eval(as.name(paste0('xT',l,'R6')))[(eval(as.name(paste0('xT',l,'RY6')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY6')))[i,1]+1500),j]
      }
    }
   # assign(paste0("L", l),list(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
  #  assign(paste0("L2", l),list(    rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6)))
    assign(paste0("M", l),rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
# could also     assign(paste0("L", l),list(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
#    assign(paste0("L", l),list(xM1,xM2,xM3,xM4,xM5,xM6))
#   rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6)
}

```

dim(L21[[1]])
dim(L1[[1]])
dim(L2[[1]])
dim(L3[[1]])
dim(L9[[1]])
rm(L28)
rm(L29)
rm(T1,T2,T3,T4,T5,T6,T7,T8,T9)
rm(L22)

c(dim(M1),dim(M2),dim(M3),dim(M4),dim(M5),dim(M6),dim(M7),dim(M8),dim(M9))

```{r}
T1Ys=matrix(NA,nrow=48*6,ncol=3)
T2Ys=matrix(NA,nrow=48*6,ncol=3)
T3Ys=matrix(NA,nrow=48*6,ncol=3)
T4Ys=matrix(NA,nrow=48*6,ncol=3)
T5Ys=matrix(NA,nrow=48*6,ncol=3)
T6Ys=matrix(NA,nrow=48*6,ncol=3)
T7Ys=matrix(NA,nrow=48*6,ncol=3)
T8Ys=matrix(NA,nrow=48*6,ncol=3)
T9Ys=matrix(NA,nrow=48*6,ncol=3)




for (i in 1:6){
  T1Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT1RY',i)))
  T2Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT2RY',i)))
  T3Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT3RY',i)))
  T4Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT4RY',i)))
  T5Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT5RY',i)))
  T6Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT6RY',i)))
  T7Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT7RY',i)))
  T8Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT8RY',i)))
  T9Ys[1:48+48*(i-1),]=eval(as.name(paste0('xT9RY',i)))
}
```


decision:
we filter by subject. (could also have filtered by training/test)
```{r}
coefs <- butter(3, c(8 / (.5 * 250), 30 / (.5 * 250)), "pass")
for(j in 1:22){ #filtering
    M1[,j]=filter(coefs$b, coefs$a, M1[,j])
    M2[,j]=filter(coefs$b, coefs$a, M2[,j])
    M3[,j]=filter(coefs$b, coefs$a, M3[,j])
    M4[,j]=filter(coefs$b, coefs$a, M4[,j])
    M5[,j]=filter(coefs$b, coefs$a, M5[,j])
    M6[,j]=filter(coefs$b, coefs$a, M6[,j])
    M7[,j]=filter(coefs$b, coefs$a, M7[,j])
    M8[,j]=filter(coefs$b, coefs$a, M8[,j])
    M9[,j]=filter(coefs$b, coefs$a, M9[,j])
}

for(k in 1:dim(M1)[1]){ #car - all have same dimension
  M1[k,]=M1[k,]-mean(M1[k,])
  M2[k,]=M2[k,]-mean(M2[k,])
  M3[k,]=M3[k,]-mean(M3[k,])
  M4[k,]=M4[k,]-mean(M4[k,])
  M5[k,]=M5[k,]-mean(M5[k,])
  M6[k,]=M6[k,]-mean(M6[k,])
  M7[k,]=M7[k,]-mean(M7[k,])
  M8[k,]=M8[k,]-mean(M8[k,])
  M9[k,]=M9[k,]-mean(M9[k,])
}
```


Now the data may be saved as 
```{r}
save(M1,M2,M3,M4,M5,M6,M7,M8,M9,file='TMs.Rdata')
save(T1Ys,T2Ys,T3Ys,T4Ys,T5Ys,T6Ys,T7Ys,T8Ys,T9Ys,file='TYs.Rdata')
```
and easily loaded in other documents

load('TMs.Rdata')