---
title: "proj8"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(signal)
library(ggplot2)
library(R.matlab)
library(randomForest)
library(fastICA)
library(coroICA)
library(plyr)
knitr::opts_chunk$set(echo = TRUE)
```

## preproc
Loading the data: Only looking at T-files for now (excluding E-files)
Only need first 22 channels and last 6 runs
already CAR and filtered (acording to subject)
```{r}
load('Tfiles.Rdata')
load('Xfiles.Rdata')
load('Labelfiles.Rdata')
```
Xtrains=rbind(M1,M2,M3,M4,M5,M6,M7,M8)
Xtests=

```{r}
XAll=list(M1,M2,M3)
XAll$M1
```


make it a bit easier

```{r}
head(M1)
  
```

```{r}
test=function(N){
  Ms=list(M1,M2)
  print()
}
```


```{r}
fastICAtester=function(M,)
Xtrains=rbind(M1,M2,M3,M4,M5,M6,M7,M8)
Xtests=M9
Ytrains=rbind(T1Ys,T2Ys,T3Ys,T4Ys,T5Ys,T6Ys,T7Ys,T8Ys)
Ytests=T9Ys
for (i in 1:22){ #i in 1:22
  Xtrains[,i]=(Xtrains[,i]-mean(Xtrains[,i]))/sd(Xtrains[,i])  
  Xtests[,i]=(Xtests[,i]-mean(Xtests[,i]))/sd(Xtests[,i])  
}

Str=fastICA(Xtrains,n.comp=5)$S #train
Ste=fastICA(Xtests,n.comp=5)$S #test
```
ready to take the bandpower
Lets just work with the M-matrices for now.

dim(Ytrains)
for(i in 1:(48*5)){
  Tr1[i,]=log(diag(var(S1[1:750+(i-1)*750,]))) #band power
}





```{r}
dim(Ytrains) #48*6*8
dim(Ytests) #48*6
Mtrains=matrix(NA,nrow=dim(Ytrains)[1],ncol=5)
Mtests=matrix(NA,nrow=dim(Ytests)[1],ncol=5)

for(i in 1:dim(Ytrains)[1]){
  Mtrains[i,]=log(diag(var(Str[1:750+(i-1)*750,]))) #band power
}
for(i in 1:dim(Ytests)[1]){
  Mtests[i,]=log(diag(var(Ste[1:750+(i-1)*750,]))) #band power
}

```

288/6/48

```{r}
Trainset=cbind(Ytrains[,2],Mtrains)
Testset=cbind(Ytests[,2],Mtests)
```

?randomForest
```{r}
rf1=randomForest(y=as.factor(Trainset[,1]),x=Trainset[,-1],importance=T,)
print(rf1)

mean(predict(rf1,newdata=Testset[,-1])==Testset[,1]) #28% test accuracy cross/subject. not good
```
giving us test-accuracy of 28%

### fastICA done properly?



```{r}
#Xtrains=rbind(M1,M2,M3,M4,M5,M6,M7,M8)
#Xtests=M9
#Ytrains=rbind(T1Ys,T2Ys,T3Ys,T4Ys,T5Ys,T6Ys,T7Ys,T8Ys)
#Ytests=T9Ys
#for (i in 1:dim(M1)[2]){ #i in 1:22
#  Xtrains[,i]=(Xtrains[,i]-mean(Xtrains[,i]))/sd(Xtrains[,i])  
#  Xtests[,i]=(Xtests[,i]-mean(Xtests[,i]))/sd(Xtests[,i])  
#}

Mp=preProcess(Xtrains,method='pca')
Mpa=predict(Mp,Xtrains)
dim(Mpa)


#7 from..
Str=fastICA(Xtrains,n.comp=dim(Mpa)[2]) #train #dim=7

dim(Mpa)
#Ste=fastICA(Xtests,n.comp=5)$S #test
Mp2=preProcess(Xtests,method='pca',pcaComp=dim(Mpa)[2])
Mpa2=predict(Mp2,Xtests)
dim(Mpa2)
```

ready to take the bandpower
Lets just work with the M-matrices for now.
?preProcess
View(Str)

dim(Ytrains)
for(i in 1:(48*5)){
  Tr1[i,]=log(diag(var(S1[1:750+(i-1)*750,]))) #band power
}

dim(Pte)
dim(Mpa2)
dim(Str$W)

```{r}
dim(Ytrains) #48*6*8
dim(Ytests) #48*6
Mtrains=matrix(NA,nrow=dim(Ytrains)[1],ncol=dim(Mpa)[2])
Mtests=matrix(NA,nrow=dim(Ytests)[1],ncol=dim(Mpa)[2])
#dim(Str$S)
Ste=Mpa2%*%Str$W
#Ste=t(Str$W%*%t(Mpa2))

for(i in 1:dim(Ytrains)[1]){
  Mtrains[i,]=log(diag(var(Str$S[1:750+(i-1)*750,]))) #band power
}
for(i in 1:dim(Ytests)[1]){
  Mtests[i,]=log(diag(var(Ste[1:750+(i-1)*750,]))) #band power
}

```

dim(Mtrains)
dim(Mtests)
?fastICA
```{r}
Trainset=cbind(Ytrains[,2],Mtrains)
Testset=cbind(Ytests[,2],Mtests)
```

?randomForest
```{r}
rf1=randomForest(y=as.factor(Trainset[,1]),x=Trainset[,-1],importance=T,)
print(rf1)

mean(predict(rf1,newdata=Testset[,-1])==Testset[,1]) #28% test accuracy cross/subject. not good
#increased to 39%

mean(predict(rf1,newdata=temp2[,-1])==temp2[,1]) #test accuracy 20% bad!

```



## COROICA

probably wanna PCA before doing coroICA....

heres coroICA:
#dim(Xtrains)
?preProcess

View(Cte)

```{r}
colnames(Xtrains)=1:22
colnames(Xtests)=1:22
dim(Xtrains)

pcaTrain=preProcess(Xtrains,method='pca',thresh = 0.95)      #pcaTrain$dim
pcaTraincomp=(predict(pcaTrain,Xtrains)) 

pcaTests=preProcess(Xtests,method='pca',pcaComp = dim(pcaTraincomp)[2])
pcaTestscomp=(predict(pcaTests,Xtests)) 

#dim(pcaTestscomp)[1]/750/48
Ctr=coroICA(pcaTraincomp,partitionsize=48*750,groupsize=750*48*6,n_components=dim(pcaTraincomp)[2],max_iter = 10000,pairing = 'neighbouring') #train #compiles forever. does compile eventually.
Cte=coroICA(pcaTestscomp,partitionsize=48*750,groupsize=48*6*750,n_components=dim(pcaTraincomp)[2],max_iter=10000,pairing='neighbouring') #test

#CtrN2=coroICA(pcaTraincomp,partitionsize=48,groupsize=48*6,n_components=dim(pcaTraincomp)[2],pairing='neighbouring',max_iter=10000,condition_threshold = 1000,minimize_loss = minimize_loss) #train #compiles forever. does compile eventually.

#CteN=coroICA(pcaTestscomp,partitionsize=48,groupsize=48*6,n_components=dim(pcaTraincomp)[2],pairing='neighbouring') #test

#CteN2=coroICA(pcaTestscomp,partitionsize=48,groupsize=48*6,n_components=dim(pcaTraincomp)[2],pairing='neighbouring',max_iter=10000,condition_threshold = 1000,minimize_loss = FALSE) #train #compiles forever. does compile eventually.

#maybe play with pairings?. They used neighbouring in the python code
CtrS=Ctr$Shat
CteS=Cte$Shat

```
Still not converging. Maybe try with maxit=10k(as in python) instead of 1k (normal)

View(Cte)
View(Ctr)
View(CteN)
View(CtrN) #converged=false
View(Ctr)
View*Ctr

#Ctr=coroICA(Xtrains,partitionsize=48,groupsize=48*6,n_components=22)$Shat #train
#Cte=coroICA(Xtests,partitionsize=48,groupsize=48*6,n.comp=5)$S #test






```{r}
dim(Ytrains) #48*6*8
dim(Ytests) #48*6
MStrains=matrix(NA,nrow=dim(Ytrains)[1],ncol=dim(CtrS)[2])
MStests=matrix(NA,nrow=dim(Ytests)[1],ncol=dim(CtrS)[2])

test1=pcaTestscomp%*%Ctr$V 
dim(Ctr$V)



for(i in 1:dim(Ytrains)[1]){
  MStrains[i,]=log(diag(var(CtrS[1:750+(i-1)*750,]))) #band power
}

#for(i in 1:dim(Ytests)[1]){
#  MStests[i,]=log(diag(var(CteS[1:750+(i-1)*750,]))) #band power
#}

test2=t(Ctr$V%*%t(pcaTestscomp))  #looks silly! but works. should be doing this i imagine!!

for(i in 1:dim(Ytests)[1]){
  MStests[i,]=log(diag(var(test2[1:750+(i-1)*750,]))) #band power
}


temp1=cbind(Ytrains[,2],MStrains)
temp2=cbind(Ytests[,2],MStests)

#?memory.limit

#memory.limit(1000000) #dirty "fix"
rfc1=randomForest(y=as.factor(temp1[,1]),x=temp1[,-1]) #OOB error rate 62%

print(rfc1) #60% oob 58%

mean(predict(rfc1,newdata=temp2[,-1])==temp2[,1]) #test accuracy 20% bad!
#25% with ctrN
#26% with convergence....................... MOTHER FUCKER
#27%. GRR
#28 with test%*% V
#35%!!! with 
#?gc()
```
Simply using Shat from coroICA does not yield much.  worse test-accuracy than with fastICA.


Ctens

?coroICA




```{r}
for(l in 1:9){  
    tmp1=matrix(NA,nrow=750*48,ncol=22)
    tmp2=matrix(NA,nrow=750*48,ncol=22)
    tmp3=matrix(NA,nrow=750*48,ncol=22)
    tmp4=matrix(NA,nrow=750*48,ncol=22)
    tmp5=matrix(NA,nrow=750*48,ncol=22)
    tmp6=matrix(NA,nrow=750*48,ncol=22)
    for (i in 1:48){
      for (j in 1:22){
         tmp1[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R1')))[(eval(as.name(paste0('T',l,'RY1')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY1')))[i,1]+1500),j]
         tmp2[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R2')))[(eval(as.name(paste0('T',l,'RY2')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY2')))[i,1]+1500),j]
         tmp3[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R3')))[(eval(as.name(paste0('T',l,'RY3')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY3')))[i,1]+1500),j]
         tmp4[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R4')))[(eval(as.name(paste0('T',l,'RY4')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY4')))[i,1]+1500),j]
         tmp5[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R5')))[(eval(as.name(paste0('T',l,'RY5')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY5')))[i,1]+1500),j]
         tmp6[((1:750)+750*(i-1)),j]=eval(as.name(paste0('T',l,'R6')))[(eval(as.name(paste0('T',l,'RY6')))[i,1]+751):(eval(as.name(paste0('xT',l,'RY6')))[i,1]+1500),j]
      }
    }
   # assign(paste0("L", l),list(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
  #  assign(paste0("L2", l),list(    rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6)))
    assign(paste0("M", l),rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
# could also     assign(paste0("L", l),list(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6))
#    assign(paste0("L", l),list(xM1,xM2,xM3,xM4,xM5,xM6))
#   rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6)
}

```

```

